\phSection{Game Books and ClueKeeper}

Each team has received multiple \textbf{Game Books}. However, there is
not enough information in this packet to begin solving any puzzles.

Once the game begins, clues will become available in the \textbf{ClueKeeper} app that
will allow players to begin solving puzzles in the packet. Once a puzzle is
solved, its solution can be submitted via the app. As time progresses, hints
for unsolved puzzles will unlock, helping teams who are stuck. The game
ends when your time in ClueKeeper has expired.

\phSection{Main Puzzles}

Once the game begins, you'll be presented with four \textbf{Main Puzzles}. 
Each Main Puzzle can be solved directly using mathematical modeling
and problem-solving abilities. Once the solution for the puzzle has been
entered into ClueKeeper, \textbf{Points} will be awarded.

\phSection{Cryptic Puzzles}

After solving each Main Puzzle, an additional
\textbf{Cryptic Puzzle} will become available to solve.
The way to solve these puzzles is left, well,
cryptic. However, your team should still be able to use your
critical thinking to extract a hidden word or phrase. Correct
solutions are worth \textbf{Points}.

\phSection{Bonus Puzzle}

Eventually a Bonus Puzzle may become unlocked
in ClueKeeper. If so, your team will be asked to optimize a certain task, and
present your solution to Game Control in person, which will be graded and
awarded \textbf{Points}.

You may submit up to three solutions throughout
the game (including any disqualified submissions), and your best solution of the
three will be counted toward your score. You must bring a device with the
ClueKeeper app with you to submit an answer before time in the app expires.

\phSection{Metapuzzle}

Once your team has several Puzzles, the final \textbf{Metapuzzle}
becomes available. Somehow, you'll be able to use the solutions to other puzzles
to solve this ``meta''. Good luck!

\phSection{Hints}

Hints may be available to you via the ClueKeeper app. Sometimes these hints
are unlocked for free, or they may deduct points from the value of that Puzzle
if used. (No points are lost for using a Hint on a Puzzle you never solve.)

Your campus may also offer hints in person by visiting Game Control.
If so, be sure to send the player who knows the most about the puzzle you're
asking a hint about, and bring the ClueKeeper app as well. Game Control's
hint will be based upon your current understanding of the puzzle, and how much
time has been spent on the puzzle (with stronger hints being given after more
time has elapsed).

\phSection{Winning the Game}

Each team can ``beat the game'' today by solving the Metapuzzle and
completing today's story.

If your campus is offering trophies for teams competing to earn
the most Points before time expires, ties will be broken based
on how earned their final Point first according to the ClueKeeper app.

\phSection{Additional Rules/Advice}

\begin{itemize}
\item Players should not do anything which
would interfere with other teams solving puzzles. Be a good sport!
\item Submissions for each non-Bonus puzzle are unlimited, but ClueKeeper
will temporarilly block submissions if too many are attempted in a short time.
Every submission for the Bonus Puzzle will be carefully graded by Game Control,
so only three submissions are allowed.
\item Before visiting Game Control to ask for a hint or clarification, make
sure you've read all the material accompanying the puzzle in the app and
on paper! Often your question will be answered there.
\item Teachers and chaperones are not allowed to help teams solve
puzzles if they are competing against other teams to earn more points.
\item Teams may use any supplies they've brought and even
look things up online to solve puzzles, but players should not receive any direct
assistance from outside their team (e.g. you can't phone a friend).
\item Players must remain within any physical boundaries set by both
Game Control and their teacher/chaperone at all times, and must always
travel with a teammate when leaving their headquarters.
\item Teachers/chaperones are responsible for their students at
all times.
\item Since this game will be played at different campuses on different
days, please do not spoil any of today's puzzles or solutions online until
the game book is released publicly by MaPP!
\item Contact Game Control immediately in the case of emergency
or any issues with these rules.
\end{itemize}

