The Galaxy Chart is referenced to unlock puzzles in ClueKeeper.
At non-GPS campuses, the name of the System is simply entered to
unlock the puzzle. At GPS campuses, each sector (letter-number pair
from the bottom/left boundaries) is associated with a location on
campus, and players must physically visit that location and check
in with GPS. 

\begin{itemize}
\item
  \textbf{Main Puzzles 1-4:} The center of the regular 3/4/5/7-gons (respectively).
  \begin{itemize}
  \item \texttt{MIRROR} (C2)
  \item \texttt{EBOBG} (C3)
  \item \texttt{OUTBID} (C1)
  \item \texttt{SPUNKY} (A3)
  \end{itemize}
\item
  \textbf{Cryptic Puzzle 1:} The system on an intersection of gridlines.
\begin{itemize}\item\texttt{GB} (D2)\end{itemize}
\item
  \textbf{Cryptic Puzzle 2:} The upper-right system in a pair that is 3000 parsecs
  apart horizontally and vertically. 
\begin{itemize}\item\texttt{SPOTLESS} (B3)\end{itemize}
\item
  \textbf{Cryptic Puzzle 3:} The system named for the word \texttt{PUZZLE} when
  ROT13 is applied. 
\begin{itemize}\item\texttt{CHYMMR} (C1)\end{itemize}
\item
  \textbf{Cryptic Puzzle 4:} The largest system in a line of four systems ordered small-to-large. 
\begin{itemize}\item\texttt{UVQQRA} (A1)\end{itemize}
\item
  \textbf{Metapuzzle (to solve):} The location where CAPSULAR/REBOOT and COAXAL/SPROUT cross.
  (Must enter \texttt{STAR} to solve.)
\begin{itemize}\item\texttt{YRSG} (C3)\end{itemize}
\item
  \textbf{Hidden Puzzle (to solve):} The lower-left system on the chart. (Must enter \texttt{ROBOT} to solve.)
\begin{itemize}\item\texttt{DULL} (A1)\end{itemize}
\end{itemize} 
